Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-06-15 Scripts/Initial_Analysis.Rmd
Juanitos map for emerging stocks

@@

results <- foreach(i=1:repetitions,
                    .combine = rbind,
                    .packages = c("MyFunctions",packages),
                    .options.snow = opts,
                   .verbose = T) %dopar% 
  GetTransIndex(
    taxon_key =spp_reman[i],
    ensemble_list = ensemble_list,
    year = year_df$year,
    Hist_y = 2000,
    data_type = "Catch",
    Neighbours = Neighbours,
    eez_centroid = eez_centroid
  )

@@

write_csv(Emerging_result,
          paste(my_path("R"),"Emerging_Results.csv",sep="")
)

# Version 1 (embeded loop) <- 3.01
# Version 2 (embeded lapply) <- 2.71
# Version 3 (embeded mclapply) <- 1.597311 mins
# Version 4 (embeded mclapply) + mclapply in spp <- 1.597311 mins

@@

# Get taxon list
Taxon_List <- list.files(paste(result_path,"/Proportion/",sep=""))

@@

### Fig.Percentage Change Map

@@

### Fig. Netowrk

@@

>>>>

```{r Emerging_routine_DoPar, eval = F, echo = F}

@@

foreach(i=1:repetitions,
        .combine = rbind,
        .packages = c("MyFunctions",packages),
        .options.snow = opts,
        .verbose = T) %dopar% 
  GetTransIndex(
    taxon_key =spp_reman[i],
    ensemble_list = ensemble_list,
    year = year_df$year,
    Hist_y = 2000,
    data_type = "Catch",
    Neighbours = Neighbours,
    eez_centroid = eez_centroid
  )

@@

@@

####  Prooportion Analysis

```{r PropChange, eval = F, echo =F}

# Get taxon list
Taxon_List <- list.files(paste(my_path("R"),"Propotion",sep=""))

@@

##### Fig.Percentage Change Map

@@

##### Fig. Netowrk

@@

####  Year of Eergence Analysis

```{r PropChange, eval = F, echo =F}

# Get taxon list
Taxon_List <- list.files(my_path("R",extra_path = "Emergence_yr"))

# clean names for function
Taxon_List <- gsub("_.*","",Taxon_List)

Paths <- paste(my_path("R",extra_path = "Emergence_yr"),Taxon_List,"_emergence.txt",sep="")

# Load all sp in noe table
Eme_Res <- bind_rows(lapply(Paths, fread))
# warnings() for empty data species

View(Eme_Res)

##### Histogram of Data

```{r histo,  eval = T, echo = T}

Eme_Res %>% 
  filter(
    n_ens == 10,
    emerging_yr >= 2020
  ) %>% 
  group_by(eez_name,emerging_yr) %>% 
  summarise(
    n_tax = length(unique(taxon_key))
  ) %>% 
  ggplot() +
  geom_histogram(
    aes(
      x = emerging_yr
    ),
    stat = "count"
  ) # +
  # facet_wrap(~n_ens)

Eme_Res %>% 
  filter(
    n_ens == 10#,
    # emerging_yr >= 2020
  ) %>% 
  group_by(emerging_yr) %>% 
  summarise(
    n_tax = length(unique(taxon_key))
  ) %>% 
  group_by() %>%
  mutate(RMean = rollmean(x = n_tax, 
                          10,
                          align = "right",
                          fill = n_tax)
  ) %>%
  filter(emerging_yr >= 2020) %>% 
  ggplot() +
  geom_line(
    aes(
      x = emerging_yr,
      y = RMean
    )
  )

##### Mapping the time of emergence

```{r time_emergence_map,  eval = T, echo = T}

results <- Eme_Res %>% 
  filter(
    n_ens == 10#,
    # emerging_yr >= 2020
  ) %>% 
  group_by(eez_name,eez_neighbour,emerging_yr) %>% 
  summarise(
    n_tax = length(unique(taxon_key))
  ) %>% 
  mutate(
    time_step = ifelse(emerging_yr <= 2050, "Mid_Century","Then_End_Century")
  ) %>% 
  # filter(
  #   emerging_yr >= 2030
  # ) %>% 
  group_by(eez_name,eez_neighbour,time_step) %>% 
  summarise(
    n_tax_emer = sum(n_tax)
  )

# Prepare data from results
Test_Data <- results %>% 
  # get coords for sources
  left_join(coords,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(coords,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  # mutate(
  #   per_mid = ifelse(is.na(per_mid),0,per_mid)
  # ) %>% 
  drop_na() #%>% 
  # filter(
    # per_mid >= 20,
    # variable == "mean_spp",
  # )

ggplot() +
  geom_sf(
    # data = subset(world_map,name %in% country),
    data = World_map,
    size = 0.1, fill = "gray90", col = "gray90") +
  geom_sf(
    # data = subset(World_eez_sf, eez_name %in% country),
    data = World_eez_sf,
    size = 0.1, fill = "white", col = "gray70") +
  geom_point(data = Test_Data,
             # data = subset(Test_Data, source %in% country & target %in% source),
             aes(start_lon,
                 start_lat,
                 col = n_tax_emer),
             size = 0.1,
             col = "black",
             # shape = 21,
             stroke = 1.5) +
  geom_path(data = paths,
            # data = subset(paths, source %in% country),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = n_tax_emer
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc")),
            show.legend = NA) +
  # geom_sf_text(data = subset(World_eez_sf, eez_name %in% country),
  #              aes(label =eez_name),
  #              size = 2) +
  # geom_text(data = subset(Test_Data, source %in% country),
  #              aes(start_lon,
  #                start_lat,
  #                label = paste(source,"to",target)
  #              ),
  #              size = 2) +
  # geom_text_repel(data = Test_Data,
  #   aes(start_lon,
# start_lat,
# label = paste(source,"to",target)
# )
# )+
ggtheme_map() +
  scale_colour_gradientn("Number of emerging stocks",
                         colours = wesanderson::wes_palette("Zissou1", 100, type = "continuous"),
                         limits = c(0,35),
                         breaks = seq(0,35,5)
  ) +
  facet_wrap(~time_step,
             ncol = 1)
